%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt]{article}
\usepackage{geometry}
\geometry{a4paper}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{sectsty}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{DejaVu Serif}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Droid Sans}
\setmonofont[Scale=MatchLowercase]{DejaVu Sans Mono}
\allsectionsfont{\normalfont\sffamily}
\raggedright

\title{Mike Raynham\\Curriculum Vitae}
\author{Mike Raynham}

\setcounter{secnumdepth}{0}
\begin{document}
\maketitle

\section{Contact}
\begin{itemize}
    \item Mike Raynham
	\item http://www.mikeraynham.co.uk
	\item enquiries@mikeraynham.co.uk
	\item +44 7813 307561
	\item 46 Bond Street, Macclesfield, SK11 6QS
\end{itemize}

\section{Summary}

\begin{itemize}
    \item Diverse experience over 22 years: 8 years using Linux, Apache, nginx and
          MySQL, plus 13 years using and supporting Windows.
    \item 3 years programming Perl and supporting Linux, Apache, nginx and MySQL for
          a high capacity website.
    \item 2 years as technical lead for a small team of developers and sysadmins.
\end{itemize}

\section{Work experience}

\subsection{SpareRoom.co.uk}
\subsubsection{August 2011 to present (Technical Lead)}

SpareRoom.co.uk is one of the busiest flatsharing websites in the UK.

\begin{itemize}
    \item Technical lead for a small team of developers and sysadmins.
    \item Introduced unit testing and developed procedures for testing and refactoring
          legacy code.
    \item Defined Perl coding standards and introduced code reviews.
    \item Drove continuous refactoring of code and simplification of server and
          application architecture, thus leading to code and servers that are easier to
          maintain.
    \item Created standardised development and testing environments using Vagrant and
          Puppet across VirtualBox and remote KVM virtual machines.
    \item Simplified the release process, making it quicker, safer and more automated.
    \item Migrated the version control system from Subversion to Git and provided
          documentation and training.
    \item Planned, tested and carried out migration of advert photo storage and
          retrieval from a dedicated server to Amazon S3, using ELB, EC2 and S3.
    \item Interviewed developers and provided training for new starters.
    \item Planned and implemented a Perl upgrade from version 5.8 to 5.18.2.
    \item Planned and implemented a database upgrade from MySQL 4.1.22 to Percona
          Server 5.6.
\end{itemize}

\subsection{Self employment}
\subsubsection{August 2005 to August 2011}

Web development and IT support for small businesses.

\begin{itemize}
    \item Created database driven websites with custom content management systems.
    \item Earlier sites used Linux, Apache, MySQL and PHP.  Later sites used Linux,
          nginx, MySQL and Perl.  For these, I utilised the Catalyst MVC framework and
          DBIx::Class.
    \item Hand-coded all HTML and CSS.
    \item Designed and produced artwork using open source tools (primarily Inkscape
          and Gimp).
\end{itemize}

Additional work included:

\begin{itemize}
    \item The development and testing of installation procedures for a Microsoft
          Silverlight IIS complaints system that had been designed for local councils
          by a software development company in Wilmslow.
    \item The development of an application for Reed Professional Services to extract
          information from their accounting system, create PDF remittance advice notes,
          and email these directly to contractors. The application processes around 300
          remittance advice notes per week.  It was written in MS Visual Basic Express,
          and used an SQLite database.
\end{itemize}

\subsection{Cheshire Building Society}
\subsubsection{July 2001 to April 2003 (Technical Support Programmer)}
\subsubsection{April 2003 to August 2005 (Infrastructure \& Security Analyst)}

Based in Technical Support, I was part of a small third level support team
responsible for the all the back end IT systems:

\begin{itemize}
    \item Testing and maintaining the disaster recovery plan.
    \item Design, installation and support for all intrusion detection, firewall and
          other security systems.
    \item Call-out support for all critical systems, including the core banking
          applications, security and intrusion detection and e-commerce systems.
    \item Providing training and support to User Support---the first and second level
          support team.
    \item Providing support to the Core Systems Development team.
\end{itemize}

Projects and responsibilities included:

\begin{itemize}
    \item Design, implementation and support of the company's anti-virus software and 
          procedures.
    \item Design, development and maintenance of a bespoke VB 6.0 application to
          install security patches and application updates, configure software and
          hardware settings and perform many other routine tasks at logon, whilst also
          providing extensive system information logs for all the company's PCs.
    \item The migration from Novell GroupWise 5.0 to Microsoft Exchange 2000 and
          Outlook 2002.  This included server installation and configuration, migration
          of user accounts, and installation of software on all user PCs.
    \item The development of a bespoke application to automatically create and
          configure Exchange/Outlook profiles for users.  It allows users to roam from
          PC to PC whilst maintaining all their settings, without the need for bloated
          Windows OS roaming profiles.  This ensured that users maintained some of the
          functionality of GroupWise, whilst also benefiting from the new features of
          Exchange and Outlook.
    \item The design and installation of a Microsoft Active Directory environment run
          in parallel with the existing Novell Directory Services during the migration.
    \item The installation, configuration and roll-out of the RIM Blackberry messaging
          system.
\end{itemize}

\subsection{Building Design Partnership}
\subsubsection{July 1996 to July 2001}

BDP is a large architectural practice, with offices throughout the country.  I
was based in the Head Office as a member of the third level support team,
Central IT Support.

\begin{itemize}
    \item Provided technical support to first and second level IT support teams.
    \item Advised on PC hardware selection and standard configuration issues.
    \item Support and coordination of BDP's anti-virus software and security systems.
    \item Day to day supervision and training of the Installations Technician.
    \item Designed validation procedures used for all specialised technical software
          within the practice.
\end{itemize}

Projects and responsibilities included:

\begin{itemize}
    \item The roll-out of Windows NT 4.0 and Windows NT 4.0 Server to all BDP offices.
    \item The development of a customised Microsoft Internet Explorer for the BDP
          Intranet.
    \item Testing and certification of all BDP's software for Year 2000 compliance.
    \item Development of Windows NT Mandatory Profiles, System Policies and logon
          scripts.
    \item Development of various bespoke utility applications using Visual Basic and
          Visual C++.
\end{itemize}

\section{Buzzwords}

Perl, MySQL, Apache, nginx, Linux, Git, Subversion, Vim, HTML, CSS,
VirtualBox, Amazon S3 (Simple Storage Services), Amazon EC2 (Elastic Cloud
Compute), AWS (Amazon Web Services), Shell Scripting, Sphinx Search, MongoDB,
PHP, Windows

\end{document}